### 2020-04-24 paper.tex
Align Readme

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give us insight in the challenges they face in their day-to-day jobs. We will evaluate and validate three scenarios extracted from their statements in order to answer \emph{RQ1}.

@@

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war stories and formalizes three recurrent challenges. With Section~\ref{sec:discussion}, we will have a look at current and previous research regarding debugging of reactive applications as well as specific tooling. We are going to validate presented challenges against currently available tools within Section~\ref{sec:study}, show threats to the validity of our work with Section~\ref{sec:threats} and finally end with an outlook on future iterations.

>>>>

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give us insight in the challenges they face in their day-to-day jobs. We will evaluate and validate three cases extracted from their statements in order to answer \emph{RQ1}.

@@

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war stories and formalizes three recurrent challenges. With Section~\ref{sec:discussion}, we will have a look at current and previous research regarding debugging of reactive applications as well as specific tooling. We are going to validate presented challenges against currently available tools within Section~\ref{sec:study}, show threats to validity of our work in Section~\ref{sec:threats} and finally end with an outlook on future iterations.
